---
title: "ECOAdS Geoportal - Tools"
subtitle: "Alessandro Oggioni & Paolo Tagliolato"
author: "CNR-IREA"
date: June 8, 2021
output:
  revealjs::revealjs_presentation:
    transition: fade
    # css: monokai.css
    center: true
    mathjax: NULL
    theme: white
    highlight: default
    self_contained: false
    reveal_plugins: ["menu", "notes"]
    reveal_options:
      slideNumber: true
      previewLinks: true
      menu:
        numbers: true
    includes:
      before_body: logoPrefix.html
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# The tools allow to:

1. Evaluate the eLTER and Natura 2000 (N2K) sites' contribution to the [Marine Strategy Framework Directive (MSFD)](https://eur-lex.europa.eu/legal-content/EN/TXT/?uri=CELEX:32008L0056) monitoring activity (**Directive contribution**)

2. Evaluate the N2K sites' contribution to the conservation of target species and habitats included in the site (**Conservation strategy**)

# 1st use case

The first use case is designed for policy maker or researchers that want to assess the contribution of a monitoring site (e.g. [Long Term Ecological Research (eLTER)](https://www.lter-europe.net/lter-europe)) to the Marine Strategy Framework Directive (MSFD).

# {data-background-iframe="https://ecoads.eu/site/96969205-cfdf-41d8-979f-ff881ea8dc8b/"}
```{r, echo=FALSE}
library(htmltools)
tags$div(
  class = "fragment fade-out",
  style = "position: absolute; width: 40%; left: 600px; bottom: 50px; box-shadow: 0 1px 4px rgba(0,0,0,0.5), 0 5px 25px rgba(0,0,0,0.2); background-color: rgba(200, 200, 200, 0.9);  padding: 20px; font-size: 20px; text-align: left;",
  tags$h2('Directive contribution tool'),
  tags$p(
    'Click on the first bullet point to access the first tool about the contribution to the Marine Strategy Framework Directive (MSFD) monitoring.'
  )
)
```

# {data-background-iframe="https://processing.get-it.it/shiny/ecoss/?siteid=2e6014fe-8f3b-4127-8ab1-405ae1303281&tab=contribution"}
```{r, echo=FALSE}
library(htmltools)
tags$div(
  class = "fragment fade-out",
  style = "position: -546px; width: 40%; left: 657px; bottom: 50px; box-shadow: 0 1px 4px rgba(0,0,0,0.5), 0 5px 25px rgba(0,0,0,0.2); background-color: rgba(200, 200, 200, 0.9);  padding: 20px; font-size: 20px; text-align: left;padding-top: 20px;margin-left: -103px;border-top-width: 0px;border-top-style: solid;margin-top: -240px;margin-right: 0px;",
  tags$h2('Directive contribution tool'),
  tags$p(
    'The graph shows the site contributing to the MSFD. The parameters listed with the green checked circle represent the parameters monitored in the site that match with those deemed necessary to contribute to the MSFD criteria. The dark blue are all the MSFD criteria to which the parameters can contribute. The lines are meant to represent the connection between the parameters and the criteria.'
  ),
  tags$p('The table below reproduces the information provided in the graph: the parameters monitored and the MSFD criteria. A link to the ECOSS thesaurus for parameters and MSFD criteria has provided.')
)
```

# 2nd use case

The second use case is designed for those managers of [Natura 2000 network](https://ec.europa.eu/environment/nature/natura2000/awards/natura-2000-network/index_en.htm) site that want to assess the contribution of the site, to the species- or habitat-conservation strategy in order to implement and/or build a Management Plan.

# {data-background-iframe="https://ecoads.eu/site/2e6014fe-8f3b-4127-8ab1-405ae1303281/"}
```{r, echo=FALSE}
library(htmltools)
tags$div(
  class = "fragment fade-out",
  style = "position: absolute; width: 40%; left: 600px; bottom: 50px; box-shadow: 0 1px 4px rgba(0,0,0,0.5), 0 5px 25px rgba(0,0,0,0.2); background-color: rgba(200, 200, 200, 0.9);  padding: 20px; font-size: 20px; text-align: left;",
  tags$h2('Conservation strategy tool'),
  tags$p(
    'Click on the second bullet point to access the second tool about the evaluation of the conservation strategy.'
  )
)
```

# {data-background-iframe="https://processing.get-it.it/shiny/ecoss/?siteid=2e6014fe-8f3b-4127-8ab1-405ae1303281&tab=conservation"}
```{r, echo=FALSE}
library(htmltools)
tags$div(
  class = "fragment fade-out",
  style = "position: -546px; width: 40%; left: 657px; bottom: 50px; box-shadow: 0 1px 4px rgba(0,0,0,0.5), 0 5px 25px rgba(0,0,0,0.2); background-color: rgba(200, 200, 200, 0.9);  padding: 20px; font-size: 20px; text-align: left;padding-top: 20px;margin-left: -103px;border-top-width: 0px;border-top-style: solid;margin-top: -240px;margin-right: 0px;",
  tags$h2('Conservation strategy tool'),
  tags$p(
    'This graph shows the site contribution to the conservation strategy. Checked circles represent the recommended variables monitored in the site, while the light-blue symbol represents a variable that is not measured. The target species protected in the site are represented by the orange icon. Finally, also the protected habitats is/are shown.'
  ),
  tags$p(
    'Target species and habitat list are retrieved in real time from the European Environmental Agency (EEA) Linked Data repository.'
  )
)
```

# {data-background-iframe="https://processing.get-it.it/shiny/ecoss/?siteid=2e6014fe-8f3b-4127-8ab1-405ae1303281&tab=conservation"}
```{r, echo=FALSE}
library(htmltools)
tags$div(
  class = "fragment fade-out",
  style = "position: -546px; width: 40%; left: 657px; bottom: 50px; box-shadow: 0 1px 4px rgba(0,0,0,0.5), 0 5px 25px rgba(0,0,0,0.2); background-color: rgba(200, 200, 200, 0.9);  padding: 20px; font-size: 20px; text-align: left;padding-top: 20px;margin-left: -103px;border-top-width: 0px;border-top-style: solid;margin-top: -240px;margin-right: 0px;",
  tags$h2('Conservation strategy tool'),
  tags$p(
    'The tables below reproduce the information provided in the graph: target species, habitat, variables measured and not measured. These variables are indicated by ECOSS as fundamental for assessing the state of conservation of the specific target species/habitat.'
  )
)
```

# Visit the ECOAdS webportal

Continue to use the tools, visit the [ECOlogical observing system in the Adriatic Sea webportal](https://ecoads.eu/)

The tools are release as open source Shiny app.
The [GitHub](https://github.com/oggioniale/ECOSS-parametersDirectives) repository is open for further insights, suggestions or information regarding future development.

# Cite the tools

To cite *ECOSS Tools* please use DOI: **10.5281/zenodo.4944268**
or Bibtex:

``` bibtex
@software{alessandro_oggioni_2021_4944268,
  author       = {Alessandro Oggioni and
                  Paolo Tagliolato},
  title        = {{oggioniale/ECOSS-parametersDirectives: First 
                   release of ECOAdS tools}},
  month        = jun,
  year         = 2021,
  publisher    = {Zenodo},
  version      = {v1.0},
  doi          = {10.5281/zenodo.4944268},
  url          = {https://doi.org/10.5281/zenodo.4944268}
}
```
